INTELLIGENT SYSTEMS

### 2021-04-18 papers/paper_9.tex
finish 9.5.3

>>>>

\subsection{EXPERIMENTAL RESULTS AND ANALYSIS}
\subsubsection{Experiment on feature map fusion in IE-CNN branch}
There are two methods for merging the outputs generated by the two pathways. 
The first, called $f_1$, performs a concatenation, while the second, called 
$f_2$, performs an element-wise sum. Table \ref{testAccuracyIE-CNN} shows the test accuracy, adopting 
the two merger strategies, on the two LFW and CASIA-WebFace datasets. 
As we can see, $f_1$ achieves the best score but on the other hand, due to the 
increase in parameters, this fusion method is time-consuming and requires a 
high computational cost.
\begin{table}[h!]
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|c|c|c|c|}
        \hline
        \bfseries{Fusion Strategy} & \bfseries{Operate Type} & \bfseries{LFW} &\bfseries{CASIA-WebFace}\\
        \hline
        $f_1$ & concatenate & \bfseries{96.23} & \bfseries{84.35}\\
        \hline
        $f_2$ & element-wise sum & 94.80 & 83.83\\
        \hline
    \end{tabular}
    \end{adjustbox}
    \caption{The test accuracy (\%) on LFW and CASIA-WebFace of IE-CNN branch with different fusion strategy.}
    \label{testAccuracyIE-CNN}
\end{table}

\subsubsection{Experimental Evaluation Index}
In order to evaluate the proposed method, two metrics are used: sensitivity (true positive rate) and accuracy. Another custom evaluation method used is that of \emph{Top1 \& Top5 precision}. In this metric $N$ represents the total number of images of a single individual, $N_1$ represents the number of images most similar (Grade1) while $N_5$ represent the least similar images (Grade5), therefore the precision is calculated as below:
\begin{equation}
    Precision_{top1}= \frac{N_1}{N}
\end{equation}
\begin{equation}
    Precision_{top5}= \frac{N_5}{N}
\end{equation}

\subsubsection{Experiments on LFW and CASIA-WebFace}
Another framework that has achieved good results in the field of similarity 
recognition is \emph{Inception-Resnet-v2} \cite{0902694022}. The performance of this method was 
compared with that of the proposed method. The triples used to train the 
models are identical (same original images, positive and negative). The number 
of images taken are divided into positive and negative. The accuracy and 
sensitivity achieved by both methods is visible in the image \ref{fig:compareV2}. Looking at 
the results, the accuracy and sensitivity achieved by the model are higher 
than those achieved by v1.
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/paper9/comparisonV2.png}
    \centering
    \caption{Comparison between v2 and the proposed methods on LFW and CASIA-WebFace datasets.}
    \label{fig:compareV2}
\end{figure}
